Using VariantSpark to learn population structure from genomic profiles

### 2015-10-26 doc/publications/Recomb15/recomb15.tex
precision/recall table

\begin{table}
\caption{Cross-validated results, mean accuracy (and standard error) on variants from chromosome 22 of 4 super-populations.}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\setlength\tabcolsep{3pt}
\begin{tabular}{lcccc}
\hline\noalign{\smallskip}
method  & ARI & error (\%) & hold out \\
RF  & 0.757 (0.011) &0.13 (0.007) & X (Y) \\
\kMeans & 0.596 (0.066) & -- & X (Y) \\
LR & 0.923 (0.015) & 0.034 (0.006) & X (Y) \\
\noalign{\smallskip}
\hline
\label{RF}
\end{tabular}
\end{center}
\end{table}

@@

>>>>

\begin{table}
\caption{Cross-validated results, mean accuracy (and standard error) on variants from chromosome 22 of 4 super-populations.}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\setlength\tabcolsep{3pt}
\begin{tabular}{lcccc}
\hline\noalign{\smallskip}
method  & ARI & error (\%) \\
RF  & 0.757 (0.011) &0.13 (0.007) \\
\kMeans & 0.596 (0.066) & -- \\
LR & 0.923 (0.015) & 0.034 (0.006) \\
\noalign{\smallskip}
\hline
\label{RF}
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}
\caption{Mean precision and recall (and standard error of mean) for each super-population across the ten logistic regression folds.}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\setlength\tabcolsep{3pt}
\begin{tabular}{lcccc}
\hline\noalign{\smallskip}
super-population  & precision & recall \\
AFR  & 0.997 (0.003) & 0.956 (0.013) \\
AMR & 0.829 (0.020) & 0.994 (0.005) \\
EAS  & 1 (0) & 1 (0) \\
EUR  & 1 (0) & 0.950 (0.015) \\
\noalign{\smallskip}
\hline
\end{tabular}
\end{center}
\end{table}
